Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2018-10-23 paper/paper.tex
small chengs to paper.tex

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (Supplementary Section 6). Intriguingly,
by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
starts to increase, reversing the trend observed at the low
$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
over diffusion flux and (ii) the concentration near the pore edge
(prefered path) greatly increases (details see Supplementary Section
SXX \todo{markr}). This level of $\psi_{\mathrm{G}}$ cannot be reached
experimentally in graphene membrane, as this requires a
$V_{\mathrm{G}}$ larger than 2.0 V, which triggers the electrochemical
reactions \cite{Toh_2011}. On the other hand, in an IFET, the electric
potential on the pore wall is considerably higher, equivalent to
$V_{\mathrm{G}}$ due to the metallic nature of gate electrode (having
an infinitely-large quantum capacitance). We therefore conclude that
the quantum capacitance-induced nonlinear damping in the surface
potential results in the observed salt rejection.  Following the above
discussions, we further investigate the physical limits for the biased
graphene nanopores. Specifically, the salt rejection characteristics
are controlled by: (i) the overlap of EDL inside the nanopore,
essentially controlled by two length scales of $\lambda_{\mathrm{D}}$
and $R_{\mathrm{G}}$, and (ii) the graphene surface potential
$\psi_{\mathrm{G}}$ controlled by $V_{\mathrm{G}}$ following
Eq. \eqref{eq:Vg}. To this end, we calculate $\psi_{\mathrm{G}}$ as a
function of $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$ (\Fig{} \ref{fig:5}a). Clearly, when the bulk
concentration $c_{0}$ increases, a higher $V_{\mathrm{G}}$ is required
to reach the same level of $\psi_{\mathrm{G}}$. Consequently, as
revealed in \Fig{} \ref{fig:5}b, the calculated salt rejection factor
$\xi$ increases with both $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and
$V_{\mathrm{G}}$, in line with the experimentally observed
$\xi - c_{0}$ dependence. We also find the overall trends for
$\psi_{\mathrm{G}}$ and $\xi$ with respect to
$\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$
= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.

>>>>

The above mechanistic findings, nevertheless, do not fully clarify the
experimentally observed reduction of diffusive flux upon
gating. Indeed, the same physical mechanism also governs the ionic
transport through an IFET, in which a nonzero electric potential at
the nanopore center usually results in an increase of ionic
conductivity \cite{Nam_2009,Lee_2015,Feng_2016}. To this end, we
further increased the graphene surface potential $\psi_{\mathrm{G}}$
considering the same system (Supplementary Section 6). Intriguingly,
by increasing $\psi_{\mathrm{G}}$ larger than 400 mV, the ionic flux
starts to increase, reversing the trend observed at the low
$\psi_{\mathrm{G}}$ regime, due to (i) the drift flux become dominant
over diffusion flux and (ii) the concentration near the pore edge
(prefered path) greatly increases (details see Supplementary Section
S6, Supplementary Figs. S8 and S9). This level of $\psi_{\mathrm{G}}$
cannot be reached experimentally in graphene membrane, as this
requires a $V_{\mathrm{G}}$ larger than 2.0 V, which triggers the
electrochemical reactions \cite{Toh_2011}. On the other hand, in an
IFET, the electric potential on the pore wall is considerably higher,
equivalent to $V_{\mathrm{G}}$ due to the metallic nature of gate
electrode (having an infinitely-large quantum capacitance). We
therefore conclude that the quantum capacitance-induced nonlinear
damping in the surface potential results in the observed salt
rejection.  Following the above discussions, we further investigate
the physical limits for the biased graphene nanopores. Specifically,
the salt rejection characteristics are controlled by: (i) the overlap
of EDL inside the nanopore, essentially controlled by two length
scales of $\lambda_{\mathrm{D}}$ and $R_{\mathrm{G}}$, and (ii) the
graphene surface potential $\psi_{\mathrm{G}}$ controlled by
$V_{\mathrm{G}}$ following Eq. \eqref{eq:Vg}. To this end, we
calculate $\psi_{\mathrm{G}}$ as a function of
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ (\Fig{}
\ref{fig:5}a). Clearly, when the bulk concentration $c_{0}$ increases,
a higher $V_{\mathrm{G}}$ is required to reach the same level of
$\psi_{\mathrm{G}}$. Consequently, as revealed in \Fig{} \ref{fig:5}b,
the calculated salt rejection factor $\xi$ increases with both
$\lambda_{\mathrm{D}} / R_{\mathrm{G}}$ and $V_{\mathrm{G}}$, in line
with the experimentally observed $\xi - c_{0}$ dependence. We also
find the overall trends for $\psi_{\mathrm{G}}$ and $\xi$ with respect
to $\lambda_{\mathrm{D}}/R_{\mathrm{G}}$ and $V_{\mathrm{G}}$ are very
similar. More importantly, based on our theoretical prediction, with
$V_{\mathrm{G}}$ = 1.25 V and $\lambda_{\mathrm{D}} / R_{\mathrm{G}}$
= 1.0, a high value of $\xi$ of $>$ 0.85 can be achieved.
